### 2015-07-01 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Buildbot ran the code beautifier.
Modif in AxiSEM/specfem coupling manual

\item[\textbullet] Go in 'EXAMPLES/coupling\_with\_EXTERNAL\_CODES/with\_AxiSEM/example\_1st\_for\_validation'

@@

\item[\textbullet] Check the file 'expand\_2D\_3D.par', cf the paths in the 3 last lines !! ==> Caution : for the tractions path (Tractions/1/), the directory need to be created !! ==> it is created in the script 'sub\_launch\_script\_for\_make\_+\_run\_expand2D3D\_and\_reformat\_Curie\_CD.sh', but if you don't use this script, you have to create the directory yourself

>>>>

\item[\textbullet] Go in 'EXAMPLES/coupling\_with\_EXTERNAL\_CODES/with\_AxiSEM/example\_1st\_for\_validation',

(OR, create another subdirectory in '[...]/with\_AxiSEM', copy files from '[...]/example\_1st\_for\_validation' and modify them if you need)

\item[\textbullet] {\color{red} CAUTION !! : Check the file 'paths\_for\_coupling\_SPECFEM3D\_AxiSEM.sh' and modify the variable 'HOME\_SPECFEM3D'} $\Longrightarrow$ this is the only path you have to modify for specfem3d

@@

\item[\textbullet] {\color{red} Check the file 'expand\_2D\_3D.par', cf THE PATHS IN THE 3 LAST LINES (normally, these are the only paths you to modify in the AxiSEM dir) !!} ==> Caution : for the tractions path (Tractions/1/), the directory need to be created !! ==>

it is created in the script 'sub\_launch\_script\_for\_make\_+\_run\_expand2D3D\_and\_reformat\_Curie\_CD.sh', but if you don't use this script, you have to create the directory yourself
